The \dealii Library, Version 9.5

### 2023-06-24 9.5/paper.tex
Update 9.5/paper.tex
Co-authored-by: Timo Heister <timo.heister@gmail.com>

Internally above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}, to actually compute intersections between two geometric entities.

>>>>

The above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()} internally to compute intersections between two geometric entities.
